---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
Sys.setlocale("LC_MESSAGES", 'en_GB.UTF-8') # Force locale
```

# janus

<!-- badges: start -->
[![R-CMD-check](https://github.com/tesselle/janus/workflows/R-CMD-check/badge.svg)](https://github.com/tesselle/janus/actions)
[![codecov](https://codecov.io/gh/tesselle/janus/branch/master/graph/badge.svg)](https://codecov.io/gh/tesselle/janus)

[![r-universe](https://tesselle.r-universe.dev/badges/janus)](https://tesselle.r-universe.dev/janus){.pkgdown-devel}

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

## Overview

A collection of [**shiny**](https://shiny.rstudio.com) application that provides graphical user interfaces for the [tesselle](https://www.tesselle.org) packages.

```{r citation, echo=FALSE, comment=''}
utils::citation("janus")
```

## Installation

You can install the latest version of **janus** from [our repository](https://tesselle.r-universe.dev) with:

```{r universe-installation, eval=FALSE}
install.packages("janus", repos = "https://tesselle.r-universe.dev")
```

## Usage

```{r shiny, eval=FALSE}
## Load the package
library(janus)

## Run the app for matrix seriation
run_app("seriation")
```

## Contributing

Please note that the **janus** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.
