---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# janus

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

## Overview

A collection of [**shiny**](https://shiny.rstudio.com) application that provides exhanced graphical user interfaces for the [tesselle](https://www.tesselle.org) packages.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/janus")
```

## Usage

```{r shiny, eval=FALSE}
## Load the package
library(janus)

## Run the app for matrix seriation
run_app("seriate")
```

## Deploy on shinyapps.io

Download the [package source](http://github.com/tesselle/janus/archive/master.zip) from GitHub, open the `janus.Rproj` in RStudio, then deploy to [shinyapps.io](https://www.shinyapps.io) (assuming [**rsconnect**](https://github.com/rstudio/rsconnect) is properly configured).

```{r deploy, eval=FALSE}
## Load package
devtools::load_all(".")

## Deploy
deploy("seriate")
```

## Contributing

Please note that the **janus** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.
